PCA

### 2019-12-02 analysis/02_PCA.Rmd
prettier plots

tsne_model <- Rtsne(euclidist, check_duplicates=FALSE, pca=TRUE, perplexity=5, theta=0.5, dims=2)
tsne_df = as.data.frame(tsne_model$Y) 
plot(tsne_df$V1, tsne_df$V2)

@@

d <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = tissue, color = treatment, alpha = sex)) +
  geom_point(size = 2) +
  mytheme() +
  labs(x = "tSNE 1", y = "tSNE 2") +
  scale_alpha_manual(values = c(0.5,1))

@@

d <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = tissue, color = treatment, alpha = sex)) +
  geom_point(size = 2) +
  mytheme() +
  labs(x = "tSNE 1", y = "tSNE 2") +
  scale_color_manual(values = colorscharmaip2) +
  scale_alpha_manual(values = c(0.5,1))

@@

ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = study, color = tissue)) +
  geom_point(size = 2) +
  mytheme() +
  scale_color_manual(values = colorstissue) +
  labs(x = "tSNE 1", y = "tSNE 2")

>>>>

@@

d <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = tissue, color = treatment)) +
  geom_point(size = 2) +
  mytheme() +
  labs(x = "tSNE 1", y = "tSNE 2") +
  scale_alpha_manual(values = c(0.5,1))

@@

d <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = tissue, color = treatment)) +
  geom_point(size = 2) +
  mytheme() +
  labs(x = "tSNE 1", y = "tSNE 2") +
  scale_color_manual(values = colorscharmaip2) +
  scale_alpha_manual(values = c(0.5,1))

@@
